Analyzing the impact of social attributes on commit integration success

### 2017-02-20 Paper/MSRChallenge2017.tex
finished reivsion of the social factors

We scraped the commit author's
\textit{username} from a commit page. If the scraper was able to find username, the
scraper went to the user's profile information
(\textit{https://github.com/\textbf{UserName}}).

@@

\begin{itemize}
\item Repositories: the repositories the developer has access to. This 
includes where the developer is the repository owner,where the developer is a 
collaborator, and repositories that the developer can access through an 
organization membership.\footnote{https://developer.github.com/v3/repos/}
\item Stars: a count of the projects the developer has stared. Starring  a project
means to showing approval of the repository and creating a bookmark for later 
access.\footnote{https://help.github.com/articles/about-stars/}
\item Followers: number of developers that that are following the author. 
\item Following: number of developers that that are being followed by the author.
\item Contributions in the last year: Number of contributions made by the author in the last year.
\end{itemize}

We also added one item from the MSR Challenge data set to the social factors:
gh\_by\_core\_team\_member.
This factor indicates if the developer making a contribution is a core member 
of that project.

>>>>

We scraped the commit author's
\textit{username} from a commit page. If the scraper was able to find the username, the
scraper went to the user's profile information
(\textit{https://github.com/\textbf{UserName}}).

@@

\begin{itemize}
\item Repositories: the repositories the developer has access to. This 
includes repositories the developer owns, repositories the developer contributes
to, and repositories for which the developer has organizational membership access.
\footnote{https://developer.github.com/v3/repos/}
\item Stars: a count of the projects the developer has stared. Starring a project
to shows approval of the repository and creates  a bookmark for later 
access.\footnote{https://help.github.com/articles/about-stars/}
\item Followers: number of developers that follow the author. 
\item Following: number of developers that the author follows 
\item Contributions in the last year: number of contributions made by the author in the last year.
\end{itemize}

We also added one item from the MSR Challenge data set to the social factors:
gh\_by\_core\_team\_member.
This factor indicates if the commit's developer is a core member 
of that project.
